Implications of animal movement rate variation in spatial patterns of seed dispersal

### 2021-08-18 Ch1_movement_rates/Ch1_Appendix_A.Rmd
Dispersion and dispersal comparison among populations

animalTraj %>% 
  left_join(., data.frame(s.id = 1:nseeds, time = grt)) %>% 
  mutate(disp = sqrt(xloc^2+yloc^2)) -> df

@@

  df %>% 
    left_join(., data.frame(s.id = 1:nseeds, time = grt)) %>% 
    mutate(disp = sqrt(xloc^2+yloc^2)) -> df

@@

weib.boot %>% 
  ggplot(., aes(x = factor(indiv), y = est.shape)) +
  geom_violin() +
  #geom_boxplot(width = 0.1) +
  stat_summary(fun.data=mean_sdl, mult=1, 
                 geom="pointrange", color="red") +
  labs(title = "Shape") +
  theme_bw() -> p1

weib.boot %>% 
  ggplot(., aes(x = factor(indiv), y = est.scale)) +
  geom_violin() +
  #geom_boxplot(width = 0.1) +
  stat_summary(fun.data=mean_sdl, mult=1, 
                 geom="pointrange", color="red") +
  labs(title = "Scale") +
  theme_bw() -> p2

@@

>>>>

animalTraj %>% 
  left_join(., data.frame(s.id = 1:nseeds, time = grt), by = "time") %>% 
  mutate(disp = sqrt(xloc^2+yloc^2)) -> df

@@

  df %>% 
    left_join(., data.frame(s.id = 1:nseeds, time = grt), by = "time") %>% 
    mutate(disp = sqrt(xloc^2+yloc^2)) -> df

@@

weib.boot %>% 
  ggplot(., aes(x = factor(indiv), y = est.shape, color = factor(indiv))) +
  geom_violin() +
  scale_color_manual(values = mycols) +
  #geom_boxplot(width = 0.1) +
  stat_summary(fun.data=mean_sdl, mult=1, 
                 geom="pointrange", color="black") +
  labs(title = "Shape") +
  theme_bw() -> p1

weib.boot %>% 
  ggplot(., aes(x = factor(indiv), y = est.scale, color = factor(indiv))) +
  geom_violin() +
  scale_color_manual(values = mycols) +
  #geom_boxplot(width = 0.1) +
  stat_summary(fun.data=mean_sdl, mult=1, 
                 geom="pointrange", color="black") +
  labs(title = "Scale") +
  theme_bw() -> p2

@@

plot_grid(p1, p2)
```
```{r}
summ.df %>% 
  mutate(popu = 1) %>% 
  bind_rows(summ.df2 %>% 
              mutate(popu = 2)) %>% 
  bind_rows(., summ.df3 %>% 
              mutate(popu = 3)) %>% 
  ggplot(., aes(y = dsprsn, x = factor(popu), color = factor(popu))) +
  geom_boxplot() +
  geom_point(color = "grey", alpha = 0.5) +
  labs(title = "Dispersion") +
  theme_bw() +
  theme(legend.position = "none") -> p1
# p1

summ.df %>% 
  mutate(popu = 1) %>% 
  bind_rows(summ.df2 %>% 
              mutate(popu = 2)) %>% 
  bind_rows(., summ.df3 %>% 
              mutate(popu = 3)) %>% 
  ggplot(., aes(y = av.disp, x = factor(popu), color = factor(popu))) +
  geom_boxplot() +
  geom_point(color = "grey", alpha = 0.5) +
  labs(title = "Average dispersal per run") +
  theme_bw() +
  theme(legend.position = "none") -> p2
# p2
